---
title: "Untitled"
author: "Alex Setmajer"
date: "11/29/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(janitor)
library(usethis)

library(beepr)
library(praise)
library(cowsay)
library(paletteer)
library(sf)
```

## beepr::beepr()
it beeps! good to use when code will take a while to run -- or anytime you want to give yourself an audio alert.

## for loop + beep (99 bottles of beer on the wall)
seq() creates a numeric sequence. 
rev() puts it in the reverse order.

```{r, eval = FALSE}
for(i in rev(seq(1:99))) {
   print(paste(i, "bottles of beer on the wall"))
}

beep(4)
```

## praise is nice

and customizable!
```{r}
praise("${EXCLAMATION}!!! This code works ${adverb_manner}!")

praise("Holy ${creating}, Batman - this code works ${ADVERB_MANNER}!")
```

## cowsay:: say to have characters say something

```{r}
say("I love tacos!", by = "shark")
```

## usethis for everything

Created to make your life easier, especially for mundane tasks.
usethis::edit_r_profile() in console to edit your r profile.

R project first, then git & GitHub repo.
- usethis:: use_git()
- usethis:: use_github()
